---
title: 'Web Scraping and Regex'
output:
  github_document:
    df_print: paged
date: "`r format(Sys.time(), '%d %B %Y')`"
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.align = 'center', echo = TRUE)
```


```{r message=FALSE, warning=FALSE}
# Importing Data-sets
library(tidyverse)
library(stringr)
data1 <- read.csv("D:\\Projects\\Web scraping, Data Cleaning and REGEX\\data\\cleandata\\angus_deaton_GoogleScholarCitations.csv", stringsAsFactors = F)
data2 <- read.csv("D:\\Projects\\Web scraping, Data Cleaning and REGEX\\data\\cleandata\\jean_tirole_GoogleScholarCitations.csv", stringsAsFactors = F)
```
  
**Ques a) For the two scholars, how many of their paper titles begin with a word that starts with a vowel, respectively?**  
  
```{r message=FALSE, warning=FALSE}
  length(which(grepl("^[aeiou]", tolower(data1$paperName))))
  length(which(grepl("^[aeiou]", tolower(data2$paperName))))
```
  
  *Answer:* For scholar Angus Deaton, there are **146** paper titles begin with a word that starts with a vowel,  
  And for scholar Jean Tirole, there are **144** paper titles begin with a word that starts with a vowel.  
    
    
**Ques b) For the two scholars, how many of their paper titles end with “s” respectively?**  
  
```{r message=FALSE, warning=FALSE}
length(which(grepl("[s]$", tolower(data1$paperName))))
length(which(grepl("[s]$", tolower(data2$paperName))))
```
  
        
  *Answer:* For scholar Angus Deaton, there are **127** paper titles ends with “s”,  
  And for scholar Jean Tirole, there are **231** paper titles ends with “s”.  
    
    
**Ques c) For the two scholars, find the longest title, respectively (“longest” in terms of number of characters).**  
  
```{r message=FALSE, warning=FALSE}
x <- data.frame(paperName=data1$paperName,chr=apply(data1,2,nchar)[,1])
which.max(x$chr)

y <- data.frame(paperName=data2$paperName,chr=apply(data2,2,nchar)[,1])
which.max(y$chr)
```
  
    
  *Answer:* For scholar Angus Deaton, the longest title is at **410th** row,  
  And for scholar Jean Tirole, the longest title is at **574th** row.  
  
      
**Ques d) For the two scholars, calculate the variable “number of punctuation symbols in the their titles”. Display summary() statistics of these variables, and the corresponding histograms..**  
  
  
  *Answer:*  
  
```{r message=FALSE, warning=FALSE}

number_of_punctuation_in_angus_deaton <- str_count(data1$paperName, "[[:punct:]]")
summary(number_of_punctuation_in_angus_deaton)
hist(number_of_punctuation_in_angus_deaton)

number_of_punctuation_in_jean_tirole <- str_count(data2$paperName, "[[:punct:]]")
summary(number_of_punctuation_in_jean_tirole)
hist(number_of_punctuation_in_jean_tirole)
```
  
    
  
  **Ques e) Remove stop words(“the”, “a”, “an”, “and”, “in”, “if”, “but”), numbers and punctuations from the titles**  
  
  *Answer:* The removal of stop words, numbers and punctuations are given below-         
```{r message=FALSE, warning=FALSE}
library(tm)
paperName <- data1$paperName
paperName = paste(paperName, collapse = ",")
paperName = tolower(paperName)
paperName <- removeWords(paperName, c("the", "a", "an", "and", "in", "if", "but"))

paperName <- gsub("[[:digit:]]","", paperName)
paperName <- gsub("[[:punct:]]","", paperName)


paperName2 <- data2$paperName
paperName2 = paste(paperName2, collapse = ",")
paperName2 = tolower(paperName2)
paperName2 <- removeWords(paperName2, c("the", "a", "an", "and", "in", "if", "but"))
paperName2 <- gsub("[[:digit:]]","", paperName2)
paperName2 <- gsub("[[:punct:]]","", paperName2)

```
  
  
  **Ques f) Excluding stop words, numbers and punctuations, what are the 10 most frequent words in scholar A’s titles?**  
    
```{r message=FALSE, warning=FALSE}
paperName = str_replace_all(paperName, pattern = "\\s+", " ")
all_titles_list1 = str_split(paperName, pattern = " ")
title_words1 = unlist(all_titles_list1)
unique_words1 = unique(title_words1)
num_unique_words1 = length(unique(title_words1))
count_words1 = rep(0, num_unique_words1)
for (i in 1:num_unique_words1) {
count_words1[i] = sum(title_words1 == unique_words1[i])
}
top_10_order1 = order(count_words1, decreasing = TRUE)[1:10]
top_10_words1 = unique_words1[top_10_order1]
top_10_words1
```
  
  
  *Answer:* Hence, the 10 most frequent words in Angus Deaton's paper titles are given above.  
  
  
**Ques g) Excluding stop words, numbers and punctuations, what are the 10 most frequent words in scholar B’s titles?**  
  
```{r message=FALSE, warning=FALSE}
paperName2 = str_replace_all(paperName2, pattern = "\\s+", " ")
all_titles_list2 = str_split(paperName2, pattern = " ")
title_words2 = unlist(all_titles_list2)
unique_words2 = unique(title_words2)
num_unique_words2 = length(unique(title_words2))
count_words2 = rep(0, num_unique_words2)
for (i in 1:num_unique_words2) {
count_words2[i] = sum(title_words2 == unique_words2[i])
}
top_10_order2 = order(count_words2, decreasing = TRUE)[1:10]
top_10_words2 = unique_words2[top_10_order2]
top_10_words2
```
  
  
*Answer:* Hence, the 10 most frequent words in Jean Tirole's paper titles are given above.  
  
    
**Data Visualization: Wordcloud** 
  
  
**Ques 1. Excluding stop words, numbers and punctuations, create two wordclouds for all thetitles of scholar A and B respectively. What's your observation from the wordcloud plots?**  
  
  
  *Answer:*  We observe from both plots that, most frequent words are **bold and bigger** than others.  
  
```{r message=FALSE, warning=FALSE}
library(wordcloud)
scholar_angus_deaton <- wordcloud(unique_words1, count_words1, scale=c(8,.2), min.freq=6,
max.words=Inf, random.order=FALSE, rot.per=.15)
scholar_jean_tirole <- wordcloud(unique_words2, count_words2, scale=c(8,.2), min.freq=6,
max.words=Inf, random.order=FALSE, rot.per=.15)
```
   
     
      
**Ques 2. Create a line plot that displays the number of the publications for the two scholars across years. What can you observe from the plot?**    
  
*Answer:* The plots are given below-      
```{r message=FALSE, warning=FALSE}
ggplot(data=data1, aes(x=year)) +
  stat_bin(bins=80, aes(y=cumsum(..count..)), geom="line", alpha=0.8) +
  ylab("Number of publications") + xlim(1965,2020) + ggtitle("Cumulative number of publications by measurement method")+
  theme_minimal()

ggplot(data=data2, aes(x=year)) +
  stat_bin(bins=80, aes(y=cumsum(..count..)), geom="line", alpha=0.8) +
  ylab("Number of publications") + xlim(1965,2020) + ggtitle("Cumulative number of publications by measurement method")+
  theme_minimal()
```
  
  
**Final Part: Report**  
  
**Q1. On average, which scholar has more co-authors?**  
  
```{r message=FALSE, warning=FALSE}
researcher1 <- data1$researcher

mean(str_count(researcher1, ",")) #average co-authors of Angus Deaton

researcher2 <- data2$researcher

mean(str_count(researcher2, ",")) #average co-authors of Jean Tirole

```
  
*Answer:* Hence, on average scholar **Angus Deaton** has more co-authors.  
  
  
**Q2. Do the two scholars have mutual friends(co-authors)? If yes, print the names of their friends.**  
  
*Answer:* Yes, both the scholars have mutual friends, the names of their friends are generated below-  
  
  
```{r message=FALSE, warning=FALSE}
coauthors1 = sapply(as.character(researcher1), strsplit, ", ")
coauthors1 = lapply(coauthors1, trimws)
coauthors.unique1 = unique(unlist(coauthors1))[order(unique(unlist(coauthors1)))]
coauthors.unique1 = coauthors.unique1[-c(1,2)]
print(coauthors.unique1)


coauthors2 = sapply(as.character(researcher2), strsplit, ", ")
coauthors2 = lapply(coauthors2, trimws)
coauthors.unique2 = unique(unlist(coauthors2))[order(unique(unlist(coauthors2)))]
coauthors.unique2 = coauthors.unique2[-c(1,2,3,4)]
print(coauthors.unique2)
```
  
  
**Q3. Did the two scholars once publish a paper together? If yes, please print the related information of that paper.**  
  
```{r message=FALSE, warning=FALSE}
str_count(researcher1, "J Tirole")
str_count(researcher2, "A Deaton")
```
  
  *Answer:* No, The two scholars never published a paper together.  

  
**Q4. What's the paper with the most co-authors?**  
  
```{r message=FALSE, warning=FALSE}
which.max((str_count(researcher1, ",")))
str_count(researcher1[377], ",")
data1[377,"paperName"]

which.max((str_count(researcher2, ",")))
str_count(researcher2[462], ",")
data2[462,"paperName"]
```
  
  
*Answer:* For scholar **Angus Deaton**, he worked on a paper named **"Attendance list"** with **8** other co-authors.  
And For scholar **Jean Tirole**, he worked on a paper named **"An Inquiry into the Nature and Causes of the Wealth of Nations"** with **7** other co-authors.  
  
  
    
**Q8. Count the total number of citations for each journal.**  
  
*Answer:* The process of counting total number of citations for each journal of both scholars is given below-  
  
  
```{r message=FALSE, warning=FALSE}
q8_1 <- data.frame(data1$journal,data1$citations)
q8_1$data1.journal <- gsub("[[:digit:]]","", q8_1$data1.journal)
q8_1$data1.journal <- gsub("[[:punct:]]","", q8_1$data1.journal)
q8_1$data1.journal <- tolower(q8_1$data1.journal)
q8_1$data1.journal <- factor(q8_1$data1.journal)
q8_1 <- q8_1 %>% mutate_all(na_if,"")
q8_1 <- q8_1[complete.cases(q8_1), ]

scholarA <- aggregate(q8_1$data1.citations,
                 by = list(q8_1$data1.journal),
                 FUN = sum)
head(scholarA)


q8_2 <- data.frame(data2$journal,data2$citations)
q8_2$data2.journal <- gsub("[[:digit:]]","", q8_2$data2.journal)
q8_2$data2.journal <- gsub("[[:punct:]]","", q8_2$data2.journal)
q8_2$data2.journal <- tolower(q8_2$data2.journal)
q8_2$data2.journal <- factor(q8_2$data2.journal)
q8_2 <- q8_2 %>% mutate_all(na_if,"")
q8_2 <- q8_2[complete.cases(q8_2), ]

scholarB <- aggregate(q8_2$data2.citations,
                 by = list(q8_2$data2.journal),
                 FUN = sum)
head(scholarB)
```
  
  
**Q9. From the citations data, which journal do you think is the most influencial in their academic field?**  
  
*Answer:*  
```{r message=FALSE, warning=FALSE}
scholarA$Group.1 <- as.character(scholarA$Group.1)
which.max(scholarA$x)
scholarA[181,1]


scholarB$Group.1 <- as.character(scholarB$Group.1)
which.max(scholarB$x)
scholarB[38,1]
```
  
For scholar **Angus Deaton**, journal **The World Bank** was the most influential in his academic field,  
For scholar **Jean Tirole**, journal **Das Summa Summarum des Management** was the most influential in his academic field.  

  