---
title: "Web Scraping and Data Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading necessary libraries  
  
```{r message=FALSE, warning=FALSE}
library(stringr)
library(R.utils)
library(rvest)
library(dplyr)
library(xml2)
library(tm)
library(ggplot2)
```
  
  
## Web scraping the billboard hot 100 page  
  
```{r message=FALSE, warning=FALSE}
an_url="https://www.billboard.com/charts/hot-100"
an = read_html(an_url)
an
str( an )


hot100.rank = an %>% 
  html_nodes('.chart-element__rank__number') %>% 
  html_text()

hot100.artist = an %>% 
  html_nodes('.text--truncate.color--secondary') %>% 
  html_text()

hot100.title = an %>% 
  html_nodes('.color--primary') %>% 
  html_text()
hot100.title =hot100.title[-c(1,2)]


df <- data.frame(hot100.rank, hot100.artist, hot100.title)
```
  
  
## Observing number of tracks of each artist  
  
```{r message=FALSE, warning=FALSE}
table(df$hot100.artist)
```
  
  
## Creating a function that will return all the songs sang by a specific artist  
  
```{r message=FALSE, warning=FALSE}
artist.func = function(write){
  
  if(write == "List"){
    result= df$hot100.artist
    return(result)
  } 
  if(nchar(write, type="chars")){
    df_song = df[ df$hot100.artist==write, ]
    result = df_song$hot100.title
    }
  else{
    result = "Invalid Input"
  }
  return(result)
}

write = "The Weeknd"

artist.func(write)
```
  
  
## Web scraping another page, cleaning and making a data frame  
  
```{r message=FALSE, warning=FALSE}
an_url2="https://www.chewy.com/b/dry-food-294"
an2 = read_html(an_url2)
an2

brand_name = an2 %>% 
  html_nodes('h2 strong') %>% 
  html_text()
brand_name = trimws(brand_name, which = c("both"), whitespace = "[ :\t\r\n]")
brand_name

prod_name = an2 %>% 
  html_nodes('.content h2') %>% 
  html_text()
prod_name
prod_name = trimws(prod_name, which = c("both"), whitespace = "[:\t\r\n]")
prod_name
prod_name = removeWords(prod_name, brand_name)
prod_name
prod_name = trimws(prod_name, which = c("both"), whitespace = "[ :\t\r\n]")
prod_name

price.auto = an2 %>% 
  html_nodes('.autoship strong') %>%
  html_text()

price.auto

price.auto = trimws(price.auto, which = c("both"), whitespace = "[ \t\r\n]")
price.auto


price.orig = an2 %>% 
  html_nodes('.price strong') %>% 
  html_text()
price.orig = trimws(price.orig, which = c("both"), whitespace = "[ \t\r\n]")
price.orig

num_review = an2 %>% 
  html_nodes('.item-rating span') %>% 
  html_text()
num_review = trimws(num_review, which = c("both"), whitespace = "[ \t\r\n]")
num_review


df2 <- cbind(brand_name, prod_name, price.auto, price.orig, num_review)
df2 <- data.frame(df2)
```
  
  
## Average number of reviews of each brand  
  
```{r message=FALSE, warning=FALSE}
df2$num_review <- as.numeric(df2$num_review)
avg_rev_brand <-  aggregate((num_review) ~ brand_name , data= df2, FUN = mean)
avg_rev_brand
```
  
  
## Subsetting the data frame only having the brand "Taste of the wild"  
  
```{r message=FALSE, warning=FALSE}
df2_tasteofthewild = df2[df2$brand_name == "Taste of the Wild",]
```
  
  
## Visualization  
  
```{r message=FALSE, warning=FALSE}
df2$price.auto <- gsub("[$]", "", df2$price.auto)
df2$price.orig <- gsub("[$]", "", df2$price.orig)

df2$price.auto <- as.numeric(df2$price.auto)
df2$price.orig <- as.numeric(df2$price.orig)


ggplot(df2) +
 aes(x = price.orig, y = price.auto, colour = brand_name) +
 geom_point(shape = "circle", 
 size = 2.8) +
 scale_color_hue(direction = 1) +
 theme_gray()
```
  
  
## Creating a variable that shows price differences  
  
```{r message=FALSE, warning=FALSE}
df2$price.diff <- df2$price.orig - df2$price.auto
df2$price.diff[is.na(df2$price.diff)] <- 0
```
  
  
## Sorting the newly created data frame  
  
```{r message=FALSE, warning=FALSE}
df2 <- arrange(df2,brand_name, prod_name)
```
  
  
## Creating a function where I'll input the number of pages to scrape and the output will be the cleaned scraped pages in a data frame  
  
```{r message=FALSE, warning=FALSE}
chewy.info = function(url){
  an2 = read_html(url)
  
  brand_name = an2 %>% 
    html_nodes('h2 strong') %>% 
    html_text()
  brand_name
  
 prod_name = an2 %>% 
  html_nodes('.content h2') %>% 
  html_text()
 
  prod_name
  prod_name = trimws(prod_name, which = c("both"), whitespace = "[:\t\r\n]")
  prod_name
  prod_name = removeWords(prod_name, brand_name)
  prod_name
  prod_name = trimws(prod_name, which = c("both"), whitespace = "[ :\t\r\n]")
  prod_name
  
  price.auto = an2 %>% 
    html_nodes('.autoship strong') %>% 
    html_text()
  price.auto = trimws(price.auto, which = c("both"), whitespace = "[ \t\r\n]")
  price.auto
  
  
  price.orig = an2 %>% 
    html_nodes('.price strong') %>% 
    html_text()
  price.orig = trimws(price.orig, which = c("both"), whitespace = "[ \t\r\n]")
  price.orig
  
  num_review = an2 %>% 
    html_nodes('.item-rating span') %>% 
    html_text()
  num_review = trimws(num_review, which = c("both"), whitespace = "[ \t\r\n]")
  num_review
  
  
  chewy.df <- cbind(brand_name, prod_name, price.auto, price.orig, num_review)
  chewy.df <- data.frame(chewy.df)
  return(chewy.df)
}

chewy.info.final = function(page_num){
  if(page_num>5 | page_num<1){
    result="Invalid input." 
  } else{
    #url = "https://www.chewy.com/b/dry-food-294"
    result = df2[,-6]
    if(page_num<=5 & page_num>1){
      for(i in 2:page_num){
        url = paste("https://www.chewy.com/b/dry-food_c294_p" , i , sep="")
        result.temp = chewy.info(url)
        result = rbind(result, result.temp)
      }
    }
  }
  return(result)
}

page_num=3
chewy.result = chewy.info.final(page_num)
head(chewy.result)
```
  


















  
